The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-16 analysis/paper/paper.qmd
Update description of stop words used

-   Three types of stop words: global, subject-specific and document stop words.
-   Global stop words:
    -   All theses were written in English, so for common English stop words the "snowball" lexicon was used
    -   Optionally, try creating a custom stop word list on the entire corpus, by removing high-frequency words, starting with 20 words and increasing by 10 until reaching words that are not appropriate as stop words
-   Subject-specific stop words:
    -   Manually constructed list, needs domain knowledge
    -   Words that are commonly used to structure a theses, such as "preface", "contents", and "introduction", were added as custom stop words
-   Document stop words:
    -   Stop words from titles and author names should only be removed from corresponding theses

>>>>

For analyses in which word-level tokenisation was chosen, stop words, i.e., common words or words that do not add much meaning, were removed in the data preparation stage. Global, subject-specific and document stop words [@hvitfeldt2021a] were differentiated. As all theses were written in English, the pre-made "snowball" lexicon was used to remove global stop words. <!-- We tried to create a custom global stop word list on the entire corpus, by removing high-frequency words, starting with 20 words and increasing by 10 until reaching words that are not appropriate as stop words, but no significant imoprvement was observed in the result. --> Subject-specific stop words, we manually constructed a list based on our domain knowledge. Words that are commonly used to structure a theses, such as "preface", "contents", and "introduction", were added as subject-specific stop words as well. Finally, titles and author names were removed as document stop words on document-level.
